Predictors of frog survival following translocations - analyses

### 2022-10-24 code/translocation_survival_analysis.Rmd
Address #10, demonstrate how to unstandardize effect plots

>>>>

Demonstrate how to unstandardize effect of elevation. This can be applied to all other effect plots.

### Try unstandardizing two ways and confirm both give the same answer

# First: Just replace elev_z with elevation
set.seed(12) # set seed for comparison between the two
d1_elevz %>% 
  select(site_id, translocation_id, snowt1_z, elev_z, male_c, donor, surv, elevation) %>% 
  add_epred_draws(m1d_reduce, ndraws = 100, re_formula = NA) %>% 
  ggplot(aes(x = elevation, y = surv)) +
    geom_line(aes(y = .epred, group = .draw), color = "blue", size = 0.2, alpha = 0.5) +
#    geom_point(aes(y = .epred)) +
  labs(x = "Elevation of recipient site (standardized)", y = "Probability of 1-year frog survival")

# Second: Untransform elev_z based on mean and sd
set.seed(12) # Same seed for comparison

# Calculate mean and sd for elevation covariate
mean_elev = mean(d1$elevation)
sd_elev = sd(d1$elevation)

d1_elevz %>% 
  select(site_id, translocation_id, snowt1_z, elev_z, male_c, donor, surv, elevation) %>% 
  add_epred_draws(m1d_reduce, ndraws = 100, re_formula = NA) %>% 
  ggplot(aes(x = (elev_z * 2*sd_elev) + mean_elev, y = surv)) +
    geom_line(aes(y = .epred, group = .draw), color = "blue", size = 0.2, alpha = 0.5) +
#    geom_point(aes(y = .epred)) +
  labs(x = "Elevation of recipient site (standardized)", y = "Probability of 1-year frog survival")

These two approaches give the same answer and can be applied to the code below.
